The five pillars of computational reproducibility: Bioinformatics and beyond

### 2023-06-10 manuscript/5pillars.Rmd
Introduce the idea of 'cumulative science'

In research, computational reproducibility is the ability to use the materials from a past study
(such as data, code and documentation) to regenerate the outputs including figures and tables to
confirm the study's findings @Goodman2016-wi.
Reproducibility is only the first step towards overall reliability, for example a study may be
reproducible, but suffer from analytical problems that invalidate the results.
If a study is reproducible, then at least these analytical issues can be more easily identified and
rectified.
Therefore, reproducibility is a necessary stepping-stone that should enhance the overall
reliability of computational research including replicability and robustness.
Replicability being defined as the ability to repeat the entire study and come up with similar overall
results.
Robustness refers to the ability for the findings to be generalisable to other situations
@Nosek2022-zc.

>>>>

In research, computational reproducibility is the ability to use the materials from a past study
(such as data, code and documentation) to regenerate the outputs including figures and tables to
confirm the study's findings @Goodman2016-wi.
Reproducibility is only the first step towards overall reliability, for example a study may be
reproducible, but suffer from analytical problems that invalidate the results.
If a study is reproducible, then at least these analytical issues can be more easily identified and
rectified.
Therefore, reproducibility is a necessary stepping-stone in the framework of cumulative science.
Reproducibility should enhance the overall reliability of computational research 
including replicability and robustness.
Replicability being defined as the ability to repeat the entire study and come up with similar overall
results.
Robustness refers to the ability for the findings to be generalisable to other situations
@Nosek2022-zc.
